Verifying Demonstrations

### 2018-11-30 paper/distance-bounding.tex
harmonization, pass 2 (still WIP)
edits pronouns, moved much of DB to LP in appendix

\Ac{DB} protocols were first suggested by \citet{DistanceBounding} to prevent relay attacks in contactless communications in which the adversary forwards a communication between a prover and a possibly far-away verifier to authenticate. 
These attacks cannot be prevented by cryptographic means as they are independent of the semantics of the messages exchanged.
As a consequence, mechanisms ensuring the physical proximity between a verifier and a prover should be used instead.
\Ac{DB} protocols precisely enable the verifier to estimate an upper bound on his distance to the prover by measuring the time-of-flight of short challenge-response messages (or rounds) exchanged during time-critical phases. 
Time critical phases are complemented by slow phases during which the time is not taking into account. 
At the end of a \Ac{DB} protocol, the verifier should be able to determine if the prover is legitimate \emph{and} in his vicinity.
In this sense, \Ac{DB} protocols combine the classical properties of authentication protocols with the possibility of verifying the physical proximity.

The main attacks against \ac{DB} protocols can be summarized as follows:
\begin{itemize}
  \item \Acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
  \item \Acf{DBMF}: the adversary illegitimately authenticates, possibly using an honest prover far away from the verifier.
  \item \Acf{DBTF}: a legitimate but malicious prover helps an accomplice close to the verifier to authenticate.
  \item \Acf{DBDH}: similar to \ac{DBDF}, the malicious prover is far away but uses an unsuspecting honest prover close to the verifier to pass as being close.
\end{itemize}
There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.

The majority of the existing \ac{DB} protocols are symmetric and thus require an honest verifier.
Indeed, in this context it does not make sense to protect against the verifier as he can easily impersonate the prover as he has a knowledge of his secret key.
There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
Our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will potentially try to \emph{impersonate the prover}.
The verifier might also try to track the provers and map their identities to their actions, thus we also require privacy.
This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{PPK}, with resistance to all the frauds mentioned above as well as against a verifier who will attempt to impersonate the prover.
More specifically, we must combine such \iac{PPK} protocol with anonymous 
credentials.
The choice of the anonymous-credential system affects the properties we 
require of the \ac{PPK}, in particular, for the suggested instantiation it must 
be \iac{PPK} for discrete logarithms.
For this paper, we assume the existence of such a protocol. Candidates for such a protocol include modifications of ~\cite{ProProx} or ~\cite{PROPS} to work for discrete logarithm and to provide general attribute-based anonymous credentials (not restricted to identity-based ones), respectively.

>>>>

Our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will potentially try to \emph{impersonate the prover}.
The verifier might also try to track the provers and map their identities to their actions, thus we also require privacy.
This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{PPK}, with resistance to all the frauds mentioned above as well as against a verifier who will attempt to impersonate the prover.
More specifically, we must combine such \iac{PPK} protocol with anonymous 
credentials.
The choice of the anonymous-credential system affects the properties we 
require of the \ac{PPK}, in particular, for the suggested instantiation it must 
be \iac{PPK} for discrete logarithms.
For this paper, we assume the existence of such a protocol. Candidates for such a protocol include modifications of ~\cite{ProProx} or \cite{PROPS} to work for discrete logarithm and to provide general attribute-based anonymous credentials (not restricted to identity-based ones), respectively.

### 2018-11-30 paper/location-proofs.tex
moves location proofs related work to appendix, adds section title for AC figures
edits pronouns, moved much of DB to LP in appendix

\subsection{Location proofs}

>>>>

%\subsection{Location proofs}
\section{Distance bounding and location proofs}
\Ac{DB} protocols were first suggested by \citet{DistanceBounding} to prevent relay attacks in contactless communications in which the adversary forwards a communication between a prover and a possibly far-away verifier to authenticate. 
These attacks cannot be prevented by cryptographic means as they are independent of the semantics of the messages exchanged.
As a consequence, mechanisms ensuring the physical proximity between a verifier and a prover should be used instead.
\Ac{DB} protocols enable the verifier to estimate an upper bound on their distance to the prover by measuring the time-of-flight of short challenge-response messages (or rounds) exchanged during time-critical phases. 
%Time critical phases are complemented by slow phases during which the time is not taking into account. 
Slow phases, during which the time is not taken into account, complement the time critical phases.
At the end of a \Ac{DB} protocol, the verifier should be able to determine if the prover is legitimate \emph{and} in their vicinity.
In this sense, \Ac{DB} protocols combine the classical properties of authentication protocols with the possibility of verifying the physical proximity.

The main attacks against \ac{DB} protocols can be summarized as follows:
\begin{itemize}
  \item \Acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
  \item \Acf{DBMF}: the adversary illegitimately authenticates, possibly using an honest prover far away from the verifier.
  \item \Acf{DBTF}: a legitimate but malicious prover helps an accomplice close to the verifier to authenticate.
  \item \Acf{DBDH}: similar to \ac{DBDF}, the malicious prover is far away but uses an unsuspecting honest prover close to the verifier to pass as being close.
\end{itemize}
There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.

The majority of the existing \ac{DB} protocols are symmetric and thus require an honest verifier.
Indeed, in this context it does not make sense to protect against the verifier as they can easily impersonate the prover as they have knowledge of their secret key.
There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
